Synthesizing Random Generators via Higher-Order Representations

### 2019-01-17 paper/main.tex
WIP

Pellentesque dapibus suscipit ligula. Donec posuere augue in quam. Etiam vel
tortor sodales tellus ultricies commodo. Suspendisse potenti. Aenean in sem ac
leo mollis blandit. Donec neque quam, dignissim in, mollis nec, sagittis eu,
wisi. Phasellus lacus. Etiam laoreet quam sed arcu. Phasellus at dui in ligula
mollis ultricies. Integer placerat tristique nisl. Praesent augue. Fusce
commodo. Vestibulum convallis, lorem a tempus semper, dui dui euismod elit,
vitae placerat urna tortor vitae lacus. Nullam libero mauris, consequat quis,
varius et, dictum id, arcu. Mauris mollis tincidunt felis. Aliquam feugiat
tellus ut neque. Nulla facilisis, risus a rhoncus fermentum, tellus tellus
lacinia purus, et dictum nunc justo sit amet elit.

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Donec hendrerit tempor
tellus. Donec pretium posuere tellus. Proin quam nisl, tincidunt et, mattis
eget, convallis nec, purus. Cum sociis natoque penatibus et magnis dis
parturient montes, nascetur ridiculus mus. Nulla posuere. Donec vitae dolor.
Nullam tristique diam non turpis. Cras placerat accumsan nulla. Nullam rutrum.
Nam vestibulum accumsan nisl.

@@

The main contribuitions of this paper are:
%
\begin{itemize}
  %
\item We identify two patological scenarios for which standard type-driven
  automatic derivation tools fail to synthesize practical random generators, due
  to a lack of either type structure or domain knowleadge (Section
  \ref{sec:randomtesting}).
  %
\item We present a generation technique able to encode stronger properties of
  the target data by reifying the static information present on the program
  codebase (Section \ref{sec:hrep}).
  %
\item We apply and extend the theory of branching processes to analitically
  predict the average distribution of generated values.
  %
  Furthermore, we use the predictions to perform simulation-based optimization
  of the random generation parameters (Section \ref{sec:synthesis}).
  %
\item We provide an implementation of our ideas in the form of a Haskell library
  to perform automatic derivation of random generators capable to extract
  useful structure information from the user source code.
  %
\end{itemize}
\section{Type-Driven Random Generation} \label{sec:randomtesting}

@@

\subsection{\textbf{Type-Driven Generation of Random Values}}

@@

\subsection{\textbf{Presence of Complex Pattern Matchings}}

@@

\subsection{\textbf{Data Invariants Encoded on Abstract Interfaces}}

@@

The key idea of this work is to represent different sources of structured value
information of a data type in a homogeneous way that we call a ``higher-level
representation'' (\ensuremath{\text{HRep}} from now on).%
\footnote{The notion of higher-level comes from that the generation process of
  given target data type is entirely determined by the type of the chosen
  representation, instead of by a concrete generator defined at the term level.}
%
For this purpose, we use a series of automatically derived data types, each one
representing an atomic unit of information that can be randomly generated and
then reflected back to the corresponding value of the original data type.

@@

\subsection{\textbf{Representing Data Constructors}}

We begin by introducing the simplest representation that we can extract from our
codebase: the representation of single data constructor.
%
Each original constructor can be represented by a automatically derived data
type consisting of a single constructor with the same fields, except for the
recursive ones that are abstracted away.
%
In this light, we represent each constructor of the data type \ensuremath{\Conid{Exp}} as follows:

@@

Note that the previous definition are type parametric over the type parameter
\ensuremath{\Varid{r}}.
%
This way we can replace \ensuremath{\Varid{r}} with any concrete data type, obtaining different
possible values on each case.
%
For instance, the value (\ensuremath{\text{Mk}_{Add}\;\mathrm{10}\;\mathrm{20}}) has type \ensuremath{\text{HRep}_{Add}\;\Conid{Int}}, while the
value (\ensuremath{\text{Mk}_{Mul}\;\Conid{True}\;\Conid{False}}) has type \ensuremath{\text{HRep}_{Mul}\;\Conid{Bool}}.
%
In practice, this parametricity let us instatiate \ensuremath{\Varid{a}} with the type of the
chosen representation (which might change according to the user demands),
without having to modify anything in the underlying machinery.

For this purpose, we employ Haskell's type classes mechanism \tocite{}.
%
We define an evaluation type class $(\Downarrow)$ which specifies how to perform
a single transformation \ensuremath{\Varid{step}} from an \ensuremath{\text{HRep}} back into a concrete value of the
target:
%
\begin{align*}
  \llbracket \_ \rrbracket_{target}\ :\ rep_{target}\ \rightarrow\ target
\end{align*}

% \begin{code}
% class (rep down target) where
%   step :: rep target -> target
% \end{code}

Then, we can define the following overloaded instances of the \ensuremath{\Varid{step}} operation
for the canonical \ensuremath{\text{HRep}} of data constructors simply by mapping each lifted
constructor back into its corresponding one.
%
\begin{alignat*}{4}
  &\evalrep{\ensuremath{\text{Mk}_{Val}}\ n\ \ \ &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Val}}\ n \\
  &\evalrep{\ensuremath{\text{Mk}_{Add}}\ x\ y   &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Add}}\ \evalrep{x}{\ensuremath{\Conid{Exp}}}\ \evalrep{y}{\ensuremath{\Conid{Exp}}} \\
  &\evalrep{\ensuremath{\text{Mk}_{Mul}}\ x\ y   &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Mul}}\ \evalrep{x}{\ensuremath{\Conid{Exp}}}\ \evalrep{y}{\ensuremath{\Conid{Exp}}}
\end{alignat*}

@@

\subsection{\textbf{Type Level Combinators}}

In order to compose the \ensuremath{\text{HRep}}s for the single data constructors already
presented, we will need to define a series of type level combinators.

In first place, we define a type combinator ($\otimes$) to tag a \ensuremath{\text{HRep}} with an
explicit generation frequency:

This combinator is evaluated back to our target data type simply by piping the
result from the inner representation.
%
It does not change the evaluation semantics, as it is only considered at
generation time:
%
\begin{align*}
  \evalrep{Freq\ x : f \otimes n}{t} = \evalrep{x : f}{t}
\end{align*}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}gen_{f \otimes n}\;gen_{r}\mathrel{=}\Conid{Term}\mathop{\mathsmaller{\langle \$ \rangle}}gen_{f}\;gen_{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

@@

When generating random values, we will only allow certain terminal
representations to be generated at the moment that the generation size gets
exhausted.
%
For this, we follow the same approach as before to define a combinator (\ensuremath{\_^\bullet})
to tag terminal representations.

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\mathbf{data}\;(f^\bullet)\;\Varid{a}\mathrel{=}\Conid{Term}\;(\Varid{f}\;\Varid{a}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{align*}
  \evalrep{Term\ x : \ensuremath{f^\bullet}}{t} = \evalrep{x : f}{t}
\end{align*}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}gen_{f^\bullet}\;gen_{r}\mathrel{=}\Conid{Term}\mathop{\mathsmaller{\langle \$ \rangle}}gen_{f}\;gen_{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

With these individual representations, we can define a type combinator
$(\oplus)$ to compose two \ensuremath{\text{HRep}}s into a single one:

Then, a composite representation can be transformed back into the concrete
target type by pattern matching on the data type variant and applying the \ensuremath{\Varid{step}}
tranformation to the inner \ensuremath{\text{HRep}}:
%
\begin{alignat*}{3}
  &\evalrep{L\ x &&: f \oplus g}{t} = \evalrep{x : f &&}{t} \\
  &\evalrep{R\ x &&: f \oplus g}{t} = \evalrep{y : g &&}{t}
\end{alignat*}

% \begin{code}
% instance Arbitrary1 (f oplus g) where
%   liftArbitrary gen_HRep
%     = frequency
%       [ (freq at_f, L <$> gen_HRep)
%       , (freq at_g, R <$> gen_HRep) ]
% \end{code} %$

With the introduced combinators, we can easily create a type synonym \ensuremath{\text{HRep}_{Exp}}
to refer to the canonical \ensuremath{\text{HRep}} of our original data type \ensuremath{\Conid{Exp}}, tagging for
instance the representation of the constuctor \ensuremath{\Conid{Add}} to be generated in with
double the frequency of rest:

\begin{align*}
  eval : Fix\ rep \rightarrow target
\end{align*}

\subsection{\textbf{Representing Pattern Matchings}}

\subsection{\textbf{Representing Abstract Interfaces}}

@@

% \begin{code}
% data (Term f) a = TagTerm (f a)

% instance (Term f down Exp) where
%   step (TagTerm f) = step f
% \end{code}
\section{Random Generators Synthesis} \label{sec:synthesis}

Aliquam erat volutpat. Nunc eleifend leo vitae magna. In id erat non orci
commodo lobortis. Proin neque massa, cursus ut, gravida ut, lobortis eget,
lacus. Sed diam. Praesent fermentum tempor tellus. Nullam tempus. Mauris ac
felis vel velit tristique imperdiet. Donec at pede. Etiam vel neque nec dui
dignissim bibendum. Vivamus id enim. Phasellus neque orci, porta a, aliquet
quis, semper a, massa. Phasellus purus. Pellentesque tristique imperdiet tortor.
Nam euismod tellus id erat.

Nullam eu ante vel est convallis dignissim. Fusce suscipit, wisi nec facilisis
facilisis, est dui fermentum leo, quis tempor ligula erat quis odio. Nunc porta
vulputate tellus. Nunc rutrum turpis sed pede. Sed bibendum. Aliquam posuere.
Nunc aliquet, augue nec adipiscing interdum, lacus tellus malesuada massa, quis
varius mi purus non odio. Pellentesque condimentum, magna ut suscipit hendrerit,
ipsum augue ornare nulla, non luctus diam neque sit amet urna. Curabitur
vulputate vestibulum lorem. Fusce sagittis, libero non molestie mollis, magna
orci ultrices dolor, at vulputate neque nulla lacinia eros. Sed id ligula quis
est convallis tempor. Curabitur lacinia pulvinar nibh. Nam a sapien.

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Donec hendrerit tempor
tellus. Donec pretium posuere tellus. Proin quam nisl, tincidunt et, mattis
eget, convallis nec, purus. Cum sociis natoque penatibus et magnis dis
parturient montes, nascetur ridiculus mus. Nulla posuere. Donec vitae dolor.
Nullam tristique diam non turpis. Cras placerat accumsan nulla. Nullam rutrum.
Nam vestibulum accumsan nisl.
% %include sections/casestudies.tex
\section{Related Work}

@@

Nullam eu ante vel est convallis dignissim. Fusce suscipit, wisi nec facilisis
facilisis, est dui fermentum leo, quis tempor ligula erat quis odio. Nunc porta
vulputate tellus. Nunc rutrum turpis sed pede. Sed bibendum. Aliquam posuere.
Nunc aliquet, augue nec adipiscing interdum, lacus tellus malesuada massa, quis
varius mi purus non odio. Pellentesque condimentum, magna ut suscipit hendrerit,
ipsum augue ornare nulla, non luctus diam neque sit amet urna. Curabitur
vulputate vestibulum lorem. Fusce sagittis, libero non molestie mollis, magna
orci ultrices dolor, at vulputate neque nulla lacinia eros. Sed id ligula quis
est convallis tempor. Curabitur lacinia pulvinar nibh. Nam a sapien.

>>>>

@@

The main contribuitions of this paper are:
%
\begin{itemize}
  %
\item We identify two patological scenarios for which standard type-driven
  automatic derivation tools fail to synthesize practical random generators, due
  to a lack of either type structure or domain knowleadge (Section
  \ref{sec:randomtesting}).
  %
\item We present a generation technique able to encode stronger properties of
  the target data type by reifying the static information present on the program
  codebase (Section \ref{sec:hrep}).
  %
\item We apply and extend the theory of branching processes to analitically
  predict the average distribution of generated values.
  %
  Furthermore, we use the predictions to perform simulation-based optimization
  of the random generation parameters (Section \ref{sec:synthesis}).
  %
\item We provide an implementation of our ideas in the form of a Haskell library
  to perform automatic derivation of random generators capable to extract useful
  structure information from the user source code.
  %
\end{itemize}
\section{Type-Driven Random Generation} \label{sec:randomtesting}

@@

\subsection*{\textbf{Type-Driven Generation of Random Values}}

@@

\subsection*{\textbf{Presence of Complex Pattern Matchings}}

@@

\subsection*{\textbf{Data Invariants Encoded on Abstract Interfaces}}

@@

The key idea of this work is to represent different sources of structured value
information of a data type in a homogeneous way that we call a ``higher-level
representation'' (\ensuremath{\text{HRep}} from now on).%
\footnote{The notion of higher-level comes from that the generation process of
  given target data type is entirely determined by the type of the chosen
  representation, instead of by a concrete generator defined at the term level.}
%
For this purpose, we use a series of automatically derived data types, each one
representing an atomic unit of information that can be randomly generated and
then reflected back to the corresponding value of the original data type.
%
Later, the user can compose these atomic representations using the provided type
level combinators in different ways into a ``generation specification'' that
completely determines the generation process.

@@

\subsection*{\textbf{Representing Data Constructors}}

We begin by introducing the simplest data type representation that we can
extract from our codebase: the representation of single data constructor.
%
Each data constructor can be represented by an automatically derived data type
consisting of a single constructor with the same fields as the original, except
for the recursive ones that are abstracted away.
%
In this light, we represent each constructor of the data type \ensuremath{\Conid{Exp}} as follows:

@@

Note that the previous definitions are type parametric over the type parameter
\ensuremath{\Varid{r}}.
%
This allow us to replace \ensuremath{\Varid{r}} with any concrete data type, obtaining different
possible values on each case.
%
For instance, the value (\ensuremath{\text{Mk}_{Add}\;\mathrm{10}\;\mathrm{20}}) has type \ensuremath{\text{HRep}_{Add}\;\Conid{Int}}, while the
value (\ensuremath{\text{Mk}_{Mul}\;\Conid{True}\;\Conid{False}}) has type \ensuremath{\text{HRep}_{Mul}\;\Conid{Bool}}.
%
In practice, this parametricity let us instatiate \ensuremath{\Varid{r}} with the type of the
chosen generation specification (which might be composed of several \ensuremath{\text{HRep}}s),
without having to modify anything in the underlying machinery.

Having the \ensuremath{\text{HRep}} of each data constructor, we can define an evaluation relation
($\evalrep{\_}{t} : \ensuremath{\text{HRep}}_f \rightarrow t$) that maps a value from each
representation \ensuremath{\Varid{f}} back to the target data type \ensuremath{\Varid{t}}.
%
Then, we simply need to translate each constructor representation back into its
corresponding one, translating the abstracted fields recursively:
%
\begin{alignat*}{4}
  &\evalrep{\ensuremath{\text{Mk}_{Val}}\ n\ \ \ &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Val}}\ n \\
  &\evalrep{\ensuremath{\text{Mk}_{Add}}\ x\ y   &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Add}}\ \evalrep{x}{Exp}\ \evalrep{y}{Exp} \\
  &\evalrep{\ensuremath{\text{Mk}_{Mul}}\ x\ y   &&}{\ensuremath{\Conid{Exp}}}
    &&= \ensuremath{\Conid{Mul}}\ \evalrep{x}{Exp}\ \evalrep{y}{Exp}
\end{alignat*}

The last missing piece is to automatically derive a random generators for each
constructor \ensuremath{\text{HRep}}.
%
For this purpose, it is important to consider that each constructor \ensuremath{\text{HRep}} has
its recursive fields abstracted away with a type parameter that will be later
instantiated with the generation specification type.
%
Given that this specification is unknown at the derivation time, we parametrize
each \ensuremath{\text{HRep}} generator with a random generator \ensuremath{gen_{r}} that is used to generate
each recursive fields:

\subsection*{\textbf{Type Level Combinators}}

In this work we define type level combinators which let the user combine the
automatically derived \ensuremath{\text{HRep}}s in several ways.
%
In first place, we define a type combinator ($\_^\bullet$) to tag a \ensuremath{\text{HRep}} to be
terminal, i.e., a representation that is allowed be generated when the
generation size gets exausted:
%
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\mathbf{data}\;(f^\bullet)\;\Varid{a}\mathrel{=}\Conid{Term}\;(\Varid{f}\;\Varid{a}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Additionally, we define a combinator ($\otimes$) to tag a \ensuremath{\text{HRep}} with an
explicit generation frequency $n$:

The previous combinators only include information relevant to the generation
process, in a sense that neither one adds new structure to the final
representation.
%
In this light, they do not alter the evaluation semantics, and we translate them
back to our target data type by evaluating the inner representation:
%
\begin{alignat*}{4}
  &\evalrep{Freq\ x &&: f \otimes n &&}{t} &&= \evalrep{x : f}{t} \\
  &\evalrep{Term\ x &&: \ensuremath{f^\bullet}    &&}{t} &&= \evalrep{x : f}{t}
\end{alignat*}

In the previous equations we explicitly annotate (using a colon) the type of the
evaluated term for clarity.
%
Later, to generate these combinators is enough to wrap a generated value from
the inner representation with the apropriate tag:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
\column{31}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}gen_{f^\bullet}\;{}\<[16]%
\>[16]{}gen_{r}{}\<[23]%
\>[23]{}\mathrel{=}\Conid{Term}{}\<[31]%
\>[31]{}\mathop{\mathsmaller{\langle \$ \rangle}}gen_{f}\;gen_{r}{}\<[E]%
\\
\>[B]{}gen_{f \otimes n}\;{}\<[16]%
\>[16]{}gen_{r}{}\<[23]%
\>[23]{}\mathrel{=}\Conid{Freq}{}\<[31]%
\>[31]{}\mathop{\mathsmaller{\langle \$ \rangle}}gen_{f}\;gen_{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Perhaps more interesting, we define a combinator $(\oplus)$ to compose two
\ensuremath{\text{HRep}}s into a single one using a sum type and representing a random choice
between them:

A composite representation built using $(\oplus)$ is transformed back into the
target data type by pattern matching on the data type variant and evaluating the
inner \ensuremath{\text{HRep}}:
%
\begin{alignat*}{3}
  &\evalrep{L\ x &&: f \oplus g}{t} = \evalrep{x : f &&}{t} \\
  &\evalrep{R\ x &&: f \oplus g}{t} = \evalrep{y : g &&}{t}
\end{alignat*}

Generating a composite \ensuremath{\text{HRep}} is slightly more complicated than before, as we
need to perform a random choice based on the generation size and the given
frequencies for each sub-represention:

The previous definition we reflect the type level frequencies of \ensuremath{\Varid{f}} and \ensuremath{\Varid{g}}
(\ensuremath{\Varid{freq}\;\textit{@}\!f} and \ensuremath{\Varid{freq}\;\textit{@}\!g}).
%
This frequency reflection defaults to $1$ if no frequency tag ($\otimes$) is
used.
%
Then we use these frequencies to generate each inner \ensuremath{\text{HRep}} in the apropriate
proportion.
%
When the generation size gets exhausted, we reflect the terminal generation
frequency of each inner \ensuremath{\text{HRep}} in the same way as before (\ensuremath{\Varid{freq0}\;\textit{@}\!f} and
\ensuremath{\Varid{freq0}\;\textit{@}\!g}).
%
This time, however, we default the frequency reflection to $0$ for any inner
that not tagged as terminal, avoiding to generate non-terminal constructions in
the last step.

With the introduced combinators, we can easily create a type synonym \ensuremath{\text{HRep}_{Exp}}
to specify a generation schema equivalent to the one seen in the concrete random
generator of type \ensuremath{\Conid{Exp}} presented in Section \ref{sec:randomtesting}:

However, a value of type \ensuremath{\text{HRep}_{Exp}} still has its recursive calls abstracted
away---the type parameter \ensuremath{\Varid{r}} is implicit in the definition of \ensuremath{\text{HRep}_{Exp}}.
%
If we want to generate recursive values using this representation we need to
introduce a last type level combinator to ``tie the knot'' recursively:

This datatype represents the \emph{fixed point} of a parametric data type \ensuremath{\Varid{f}},
i.e., a data type where each recursive call gets instantiated with iself.
%
To translate fixed points back to our target data type we simply need translate
the inner representation:
%
\begin{align*}
  \evalrep{Fix\ x : Fix\ f}{t} = \evalrep{x : f}{t}
\end{align*}
%
Categorically, this generic transformation of fixed points is called a
\emph{catamorphism}, where our evaluation relation is known as its
\emph{algebra}.

Unlike the other combinators, to randomly generate a fixed point of a certain
representation \ensuremath{\Varid{f}}, we do not parametrize the generation of the recursive fields
of the inner represention over an external generator \ensuremath{gen_{r}}.
%
Instead, we can also tie the recursive knot in our random generator by piping
the generation of the inner \ensuremath{\text{HRep}} parametrized recursively by the itself:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}genFix_{f}\mathrel{=}\Conid{Fix}\mathop{\mathsmaller{\langle \$ \rangle}}gen_{f}\;genFix_{f}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
 %$

This way we obtain a concrete recursive generator for each representation \ensuremath{\Varid{f}}
that we define.
%
With this generator, we can define a random generator for our target data type
simply by evaluating a random value of the representation:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}gen_{Exp}\mathrel{=}\mathbf{do}\;{}\<[17]%
\>[17]{}\Varid{x}\leftarrow genFix_{(\text{HRep}\,{Exp})}{}\<[E]%
\\
\>[17]{}\Varid{return}\;\evalrep{x}{Exp}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
 %$

\subsection*{\textbf{Representing Pattern Matchings}}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
\column{52}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}gen_{foo\#1}\;{}\<[14]%
\>[14]{}gen_{r}{}\<[21]%
\>[21]{}\mathrel{=}\text{Mk}_{foo\#1}{}\<[33]%
\>[33]{}\mathop{\mathsmaller{\langle \$ \rangle}}\Varid{smaller}\;gen_{r}{}\<[52]%
\>[52]{}\mathop{\mathsmaller{\langle \ast \rangle}}\Varid{smaller}\;gen_{r}{}\<[E]%
\\
\>[3]{}gen_{foo\#2}\;{}\<[14]%
\>[14]{}gen_{r}{}\<[21]%
\>[21]{}\mathrel{=}\text{Mk}_{foo\#2}{}\<[33]%
\>[33]{}\mathop{\mathsmaller{\langle \$ \rangle}}\Varid{arbitrary}{}\<[52]%
\>[52]{}\mathop{\mathsmaller{\langle \ast \rangle}}\Varid{smaller}\;gen_{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
 %$

\subsection*{\textbf{Representing Abstract Interfaces}}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}gen_{ten}\;{}\<[15]%
\>[15]{}gen_{r}{}\<[22]%
\>[22]{}\mathrel{=}\text{Mk}_{ten}{}\<[E]%
\\
\>[3]{}gen_{square}\;{}\<[15]%
\>[15]{}gen_{r}{}\<[22]%
\>[22]{}\mathrel{=}\text{Mk}_{square}{}\<[35]%
\>[35]{}\mathop{\mathsmaller{\langle \$ \rangle}}\Varid{smaller}\;gen_{r}{}\<[E]%
\\
\>[3]{}gen_{minus}\;{}\<[14]%
\>[14]{}gen_{r}{}\<[22]%
\>[22]{}\mathrel{=}\text{Mk}_{minus}{}\<[35]%
\>[35]{}\mathop{\mathsmaller{\langle \$ \rangle}}\Varid{smaller}\;gen_{r}{}\<[54]%
\>[54]{}\mathop{\mathsmaller{\langle \ast \rangle}}\Varid{smaller}\;gen_{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
 %$

% \begin{align*}
%   \llbracket \_ \rrbracket_{target}\ :\ rep_{target}\ \rightarrow\ target
% \end{align*}
%
% \begin{code}
% class (rep down target) where
%   step :: rep target -> target
% \end{code}
%
% \begin{code}
% data (Term f) a = TagTerm (f a)

@@

@@

% instance (Term f down Exp) where
%   step (TagTerm f) = step f
% \end{code}

@@

% \begin{code}
% instance Arbitrary1 (f oplus g) where
%   liftArbitrary gen_HRep
%     = frequency
%       [ (freq at_f, L <$> gen_HRep)
%       , (freq at_g, R <$> gen_HRep) ]
% \end{code} %$
\section{Random Generators Synthesis} \label{sec:synthesis}

Aliquam erat volutpat. Nunc eleifend leo vitae magna. In id erat non orci
commodo lobortis. Proin neque massa, cursus ut, gravida ut, lobortis eget,
lacus. Sed diam. Praesent fermentum tempor tellus. Nullam tempus. Mauris ac
felis vel velit tristique imperdiet. Donec at pede. Etiam vel neque nec dui
dignissim bibendum. Vivamus id enim. Phasellus neque orci, porta a, aliquet
quis, semper a, massa. Phasellus purus. Pellentesque tristique imperdiet tortor.
Nam euismod tellus id erat.
% %include sections/casestudies.tex
\section{Related Work}

@@

Nullam eu ante vel est convallis dignissim. Fusce suscipit, wisi nec facilisis
facilisis, est dui fermentum leo, quis tempor ligula erat quis odio. Nunc porta
vulputate tellus. Nunc rutrum turpis sed pede. Sed bibendum. Aliquam posuere.
Nunc aliquet, augue nec adipiscing interdum, lacus tellus malesuada massa, quis
varius mi purus non odio. Pellentesque condimentum, magna ut suscipit hendrerit,
ipsum augue ornare nulla, non luctus diam neque sit amet urna. Curabitur
vulputate vestibulum lorem.
